How to compute the fusion product of MV cycles in type A

### 2021-04-12 draft.tex
joel fixed es section

Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
\jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$? Was $k = m$ replaced because $m$ is already used?}

@@

Let $ z \in \AA^k$. Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities. There exist unique $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a minimal length permutation  $ p $ of $ \{1, \dots, k\}$ such that 
$$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,. $$

@@

\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}

Next for $ j = 1, \dots r $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
$$
    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
    r_{z,j}(i):= N - r(p(k_j)) + r(p(k_j + i)) \, . 
$$
\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}

@@

For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduce the permutation $ p$, that $ r = 2 $, and that
\begin{equation} 
    \label{eq:rcols}
\begin{split}
        r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
        r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
\end{split}
\end{equation}
On the other hand, for $z(0)$, we get that $ r = 1$ and that 
\begin{equation} \label{eq:rcol2}
r_{z(0),1}(i) = r(i) = 
 N - 
     \#\text{~boxes in first $i$ columns of }\lambda\,. 
\end{equation}
\jcom{Someone should check that I chose the notation correctly to make this work out.}

@@

>>>>

Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
\jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$? Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes}

@@

Let $ z \in \AA^k$. Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities. There exist $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a permutation  $ p $ of $ \{1, \dots, k\}$ such that 
$$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,. $$ We require that $ p $ is of minimal length, given the choice of $ s_1, \dots, s_r$.  The data $s_\bullet, p, k_\bullet$ is unique up to a permutation of $ \{1, \dots, k\}$.

@@

\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}

Next for $ j = 1, \dots r $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
$$
    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
    r_{z,j}(i):= N + \sum_{a = 1}^i r(p(k_j + a)) - r(p(k_j +a) - 1)  \, . 
$$
\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
\jcom{I fixed it now.  I didn't want to use ES's $a_i$.}

@@

For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of $ r = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.  We also see that
\begin{equation} 
    \label{eq:rcols}
\begin{split}
        r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
        r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
\end{split}
\end{equation}
On the other hand, for $z(0)$, we get that $ r = 1$ and that 
\begin{equation} \label{eq:rcol2}
r_{z(0),1}(i) = r(i) = 
 N - 
     \#\text{~boxes in first $i$ columns of }\lambda\,. 
\end{equation}
\jcom{Someone should check that I chose the notation correctly to make this work out.}

@@

\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.  I changed the wording of ``reproduce''. I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}
